### 2018-10-26 Latex/article.tex
Edits which should have been included for sure, but did not make the cut

Finally, we present energy and dissipation spectra. As expected, we found that APE and KE
spectra were almost identical, why we only plot the
total spectra. In figure~\ref{fig_spectra_c40} we see  compensated and
normalised energy spectra from the three highest resolution runs. The
compensated spectra are almost flat in a broad range. In the high wave number
end the compensated spectra show a `bottleneck', which we interpret as a
signature of the shocks. The $ k^{-2} $-dependence and the associated scaling predicted
by (\ref{Spectra}) are very well satisfied in a limited range of high wave
numbers close to the bottleneck. At smaller wave numbers the spectra are
becoming somewhat steeper than $ k^{-2} $ and the spectrum from the run with
largest $ c $ does not collapse perfectly onto the other two spectra.  In figure \ref{fig_disspectra}
 we see normalised dissipation spectra for fixed $ c= 20 $ and different $ n $ to the left, and fixed $ n = 1920 $
and different $ c $ to the right. First we note that the spectra go to zero quite nicely for large $ k $, indicating that the shock width $ \delta x $ is well resolved. Second, we note that there is a slight shift of the maximum in both figures, even though we have normalised the wave number by $ k_d = 1/\eta_8 $.   These shifts may be explained by the estimate (\ref{EtaEight}) predicting that $ \delta x $ should vary slightly with $ d $. If the maximum of the dissipation spectra is associated with $ \delta x $, there should be a shift of the maximum  to the right with increasing $ n $ and to the left with increasing $ c $, since $ d \propto c^{-1/2} $.
 The ratio between the maximum and the minimum $ n $ in the left figure is equal to 8 and  according to (\ref{EtaEight}) the corresponding ratio between the wave numbers at which the maxima are observed should be $ 8^{1/21} \approx 1.1 $, which is exactly the value we observe. The ratio between the maximum and minimum $ c $ in the right figure is equal to $ 70 $. Assuming that $ d \propto c^{-1/2} $ the ratio between the wave numbers at which the maxima are observed should be $ 70^{1/42} \approx 1.1 $, while the observed ratio is equal to $ 1.16 $.

@@

The question that originally motivated this study was if SW wave turbulence can
be used as a model for energy dissipation in the atmosphere and the oceans.
Undoubtedly, the answer to this question is negative and the reason for this is
not primarily the appearance of shocks and the associated $ k^{-2} $-spectrum
which is not consistent with the observed $ k^{-5/3} $-spectrum. The main
reason is that SW wave turbulence is a far too inefficient agent of
dissipation. Since the Reynolds number of geophysical flows is extremely large
and the stratification is strong, the relation (\ref{Dissipation}) implies that
dissipation would be absent in the interior of the atmosphere and the oceans
with SW turbulence as the responsible agent. This not what we observe. In a companion paper \cite[]{LindborgMohanan}
we develop a toy model of geophysical turbulence which is similar to the SW equations in the mathematical structure, but is absent of shocks. 
In this model energy is dissipated through a local cascade involving both vortical and wave modes.

>>>>

Finally, we present energy and dissipation spectra. As expected, we found that APE and KE
spectra were almost identical, and therefore we only plot the
total spectra. In figure~\ref{fig_spectra_c40} we see  compensated and
normalised energy spectra from the three highest resolution runs. The
compensated spectra are almost flat in a broad range. In the high wave number
end the compensated spectra show a `bottleneck', which we interpret as a
signature of the shocks. The $ k^{-2} $-dependence and the associated scaling predicted
by (\ref{Spectra}) are very well satisfied in a limited range of high wave
numbers close to the bottleneck. At smaller wave numbers the spectra are
becoming somewhat steeper than $ k^{-2} $ and the spectrum from the run with
largest $ c $ does not collapse perfectly onto the other two spectra.  In figure \ref{fig_disspectra}
 we see normalised dissipation spectra for fixed $ c= 20 $ and different $ n $ to the left, and fixed $ n = 1920 $
and different $ c $ to the right. First we note that the spectra go to zero quite nicely for large $ k $, indicating that the shock width $ \delta x $ is well resolved. Second, we note that there is a slight shift of the maximum in both figures, even though we have normalised the wave number by $ k_d = 1/\eta_8 $.   These shifts may be explained by the estimate (\ref{EtaEight}) predicting that $ \delta x $ should vary slightly with $ d $. If the maximum of the dissipation spectra is associated with $ \delta x $, there should be a shift of the maximum  to the right with increasing $ n $ and to the left with increasing $ c $, since $ d \propto c^{-1/2} $.
 The ratio between the maximum and the minimum $ n $ in the left figure is equal to 8 and  according to (\ref{EtaEight}) the corresponding ratio between the wave numbers at which the maxima are observed should be $ 8^{1/21} \approx 1.1 $, which is exactly the value we observe. The ratio between the maximum and minimum $ c $ in the right figure is equal to $ 70 $. Assuming that $ d \propto c^{-1/2} $ the ratio between the wave numbers at which the maxima are observed should be $ 70^{1/42} \approx 1.1 $, while the observed ratio is equal to $ 1.16 $.

@@

The question that originally motivated this study was if SW wave turbulence can
be used as a model for energy dissipation in the atmosphere and the oceans.
Undoubtedly, the answer to this question is negative and the reason for this is
not primarily the appearance of shocks and the associated $ k^{-2} $-spectrum
which is not consistent with the observed $ k^{-5/3} $-spectrum. The main
reason is that SW wave turbulence is a far too inefficient agent of
dissipation. Since the Reynolds number of geophysical flows is extremely large
and the stratification is strong, the relation (\ref{Dissipation}) implies that
dissipation would be absent in the interior of the atmosphere and the oceans
with SW turbulence as the responsible agent. This is not what we observe. In a companion paper \cite[]{LindborgMohanan}
we develop a toy model of geophysical turbulence which is similar to the SW equations in the mathematical structure, but is absent of shocks. 
In this model, energy is dissipated through a local cascade involving both vortical and wave modes.
